Matching Bullets

### 2015-12-11 imaging-paper.Rnw
citations connected to previous word

Rough outline:
\begin{enumerate}
\item DONE Description of the problem: Standard operating practice, 2009 NAS report
\item DONE Description of the Results
\item DONE Walkthrough of the process
\item \hh{XXX Alternative approaches: IBIS database and the NRC report\cite{nap:2008} against it\footnote{Fox report on the NRC report \url{http://goo.gl/XurSVl}.
NRC report: \url{http://www.nap.edu/catalog/12162/ballistic-imaging}} }
\end{enumerate}

Bullet matching is a process in forensic science done to determine whether two bullets were fired from the same gun barrel. This process has broad applicability in terms of the conviction of criminals in the United States criminal justice system. Ballistics identification has long been considered an accepted and reliable procedure, but in the past ten years has undergone more significant scrutiny. In 2005, in \emph{United States vs. Green}, the court ruled that the expert could not confirm that the bullet casings came from a specific weapon with certainty, but could merely describe other casings which are similar. Further court cases in the late 2000s expressed caution about the use of ballistics identification evidence \cite{giannelli:2011}.

The new scrutiny of the procedure culminated with the 2009 National Academy of Sciences report \cite{NAS:2009}. The report concluded that minimal research had been done exploring the reliability of these ballistic identification methods. In fact, the report says the forensic evidence ``including, for example, bite marks and firearm and toolmark identification is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline."

Rifling in the barrel creates striation marks on the bullet during the firing process (and grooves). These marks are claimed to be unique to the barrel, as described in a 1992 AFTE article \cite{afte:1992}. ``The theory of identification as it pertains to the comparison of toolmarks enables opinions of common origin to be made when the \emph{unique surface contours} of two toolmarks are in sufficient agreement" The article goes on to state that ``Significance is determined by the comparative examination of two or more sets of surface contour patterns comprised of individual peaks, ridges and furrows." %\footnote{\url{https://www.ncjrs.gov/app/publications/Abstract.aspx?id=254151}}

@@

\section{Methodology}
Throughout this paper, we will work with images from the James Hamby Consecutively Rifled Ruger Barrel Study \cite{hamby:2009}. Ten consecutively rifled Ruger P-85 pistol barrels were obtained from the manufacturer and fired to produce known test bullets and unknown bullets for comparison.

@@

The ``smoothing factor" described in the algorithm represents the window size to use for a rolling average. Higher values of the smoothing factor therefore lead to more smoothed results. In the groove detection portion of this algorithm, we wish to remove most of the deviation but still maintain enough signal in the groove to detect it. Empirically, a value of 35 for the smoothing factor seems to work quite well (later in the manuscript we investigate varying the smoothing factor). It is important to note that the smoothing pass is done twice. That is, the smoothed data is once again smoothed by computing a new rolling average with the same smoothing factor. This bears some similarities to the ideas of John Tukey in his book Exploratory Data Analysis, where he describes a smoothing process called ``twicing" in which a second pass is made on the residuals computed from the first pass and then added back to the result \cite{tukey:1977}. This has the effect of introducing a little bit more variance into the smoothed data. We instead performed a second smoothing pass on the smoothed data, which has the effect of weighting observations near the center highest, while the weights linearly drop off as you reach the end of the smoothing window or smoothing factor.

@@

\section{Web Application}
We have implemented a web interface to automate many of the steps outlined in the previous section. The web interface, developed using Shiny \cite{shiny}, allows a user to upload two x3p files representing scans of a bullet between two grooves. A 3D viewer, using Plotly \cite{plotly}, allows the user to rotate and zoom to examine surface features of the images. A screenshot of the application is available in Figure \ref{fig:app}. The application is available at the url \url{http://erichare.shinyapps.io/x3prproto}.

@@

Figure~\ref{fig:match} gives an overview of the automated matching routine: 
We first identify a stable region for each bullet and pick the lowest crosscut level in this region \hh{(assumption here: lower crosscut levels show better expression of individual marks XXX need to still check)}

All of the other steps are done on pairs of bullet lands:
\begin{enumerate}
\item Smooth the two crosscuts by a loess with a very small span (see Figure~\ref{fig:smooth}). 
\item Use cross-correlation to find the best alignment along the crosscuts: Shift one of the crosscuts by the lag indicated by the cross-correlation function (see Figure~\ref{fig:ccf} for the cross-correlation function and Figure~\ref{fig:crosscutX} for the resulting shift).
\item Using a rolling average, identify peaks and grooves for each of the crosscuts. We define a region around the extrema on each side as one third of the distance to the next extrema (see Figure~\ref{fig:smoothcutb}). 
\item Match grooves and peaks between crosscuts: based on the regions around the extrema as defined above, we identify joint regions between two crosscuts as those areas, in which at least two of the individual regions touch. A joint region is defined as the smallest interval that covers all of the touching regions. A joint region is called a match between the crosscuts, if all of the crosscut-specific regions are of the same type of extrema, i.e.\ either all peaks or all valleys. In Figure~\ref{fig:match} all matches are colored corresponding to their type of extrema. Non-matching regions are left grey.
\item Identify the maximal number of CMS (consecutive matching striae) between the two crosscuts by counting consecutive matching lines. 
In the example of Figure~\ref{fig:match}, the number of consecutive matching striations (CMS) is fifteen, a  high number indicative of a match between the bullets. For lead bullets, such as this, Biasotti \cite{biasotti:1959} considered four or more consecutive lines to be sufficient evidence of a match, and which are part of current practice in assessing bullet matches  \cite{nichols:1997, nichols:2003}.
\end{enumerate}

@@

Figure~\ref{fig:cms} shows the strong connection between the maximal number of consecutive striae and matches in the Hamby study. All 29 pairs of lands with at least sixteen CMS in common are matches. There are two things that should be noted at this point: the automated algorithm finds a relatively high number of CMS even for non-matches. On average, there are 2.2 maximal CMS between known non-matches (with a standard deviation of 1.4). Known matches share on average 8.2 maximal CMS, with a standard deviation of 5.8. Secondly, a large number of maximal CMS by itself is not indicative of a match, as was previously pointed out by Miller \cite{miller:1998}. Figure~\ref{fig:mismatch} shows a known mismatch, between two lands that share fifteen consecutively matched striae. The number of peaks and valleys, their heights and depths as well as the overall pattern are in relative good agreement. \hh{XXX something re-assuring that visually we can tell them apart? I don't know - this could just as well be a case where the crosscuts are very different. }
%
\begin{figure}[hbtp]
\begin{subfigure}[t]{\linewidth}
\caption{Distribution of maximal CMS.}
<<cms-bars, echo=FALSE, fig.width=7, fig.height=3.5, out.width='\\linewidth'>>=
bstats <- read.csv("data-35-25/bullet-stats.csv")
ggplot(data=bstats) + 
  geom_bar(aes(x=factor(cms))) + theme_bw() +
  theme(legend.position="bottom") + 
  xlab("maximum CMS")
@
\end{subfigure}
\begin{subfigure}[t]{\linewidth}
\caption{All land-to-land comparisons a maximum number of CMS of sixteen or more are matches.}
<<cms-spines, echo=FALSE,  fig.width=7, fig.height=3.5, out.width='\\linewidth'>>=
ggplot(data=bstats) + 
  geom_bar(aes(x=factor(cms), fill=match), position="fill") +
  theme(legend.position="bottom") + 
  scale_fill_brewer(palette="Paired") +
  xlab("maximum CMS")
@
\end{subfigure}
\caption{\label{fig:cms}Overview of the maximal number of consecutive maximal striae compared to matches.}
\end{figure}

@@

Using recursive partitioning, we fit a decision tree \cite{breiman:1984, rpart, rpart.plot} to predict matches between lands based on features derived from the image files. The resulting tree is shown in Figure~\ref{fig:tree}. A total of 123 lands is being matched correctly. Interestingly, the number of consecutive matching striae only features as the last step in this evaluation. At this point in the tree, the first false positive matches are introduced into the results: out of the ten land-to-land comparisons three are mis-matched.
Instead of CMS, cross-correlation (ccf) between the crosscuts is very important in the matching process  by the decision tree. Aside from  cross correlation, the number of matches (num.matches) between crosscuts and the distance between crosscuts (distr.dist) is involved in the decision. 
Within matches and non-matches, the values of CMS and cross-correlation seem to be almost independent (see Figure~\ref{fig:ccfs-match}), but both are highly predictive in distinguishing matches from non-matches. Out of the two, cross-correlation has higher  predictive power. This  does not  contradict earlier findings emphasizing the value of CMS on visual assessments of bullet matches: in those papers, assessments were based on purely visual inspection of either actual bullets or 2d microscopic images of bullets.
Neither one of these methods allows for an assessment of cross-correlations. This is one of the benefits of switching to a digitalized version of the images that preserves the 3d surface structure.

@@

Another benefit is that we can not only apply a single decision tree, but several hundred of them to combine in a random forest \cite{breiman:2001, randomForest}. In a random forest multiple trees are fitted. For each of these trees, only two thirds of the observations are used for fitting, while predictions for the remaining third  are used to evaluate the tree's predictive power and accuracy, or its reverse, the error rate. Because errors are determined from the one third of held-back observations, this error rate is called the out-of bag (OOB) error. 
Figure~\ref{fig:oob} shows the cumulative out-of-bag error (OOB) rate for 300 trees. 
%
\begin{figure}[hbtp]
<<oob, echo=FALSE, fig.width=7, fig.height=3, out.width='\\linewidth'>>=
qplot(id, OOB, geom="line", data=errors) + theme_bw() + ylim(c(0,NA)) + xlab("Number of trees") + ylab("Out of Bag Error (OOB)")
@
\caption{\label{fig:oob}Cumulative out-of-bag error rate of a random forest fit to predict land-to-land matches from image features.}
\end{figure}
%
After about 25 trees, the error rate of land-to-land comparisons stabilizes at 0.0056. This is a weighted average between false positives of 0.00028 and false negatives of 0.32. Note that these error rates are based on land-to-land comparisons and will be much lower for bullet-to-bullet matches. In the case of the Hamby study, the error rate is zero, if we require for a bullet match that at least two of a bullet's lands are matched (see Figure~\ref{fig:treeresult}). 
\begin{figure}[hbtp]
<<overall-tree, echo=FALSE, fig.width=7, fig.height=4, out.width='\\linewidth'>>=
CCFs$bullet <- gsub("-[0-9]$", "", CCFs$b2)
bullets <- CCFs %>% group_by(bullet) %>% summarize(
  n = n(),
  pred = sum(pred > 0.5),
  forest = sum(forest > 0.5)
)
library(reshape2)
bm <- melt(data=bullets, id.var=c("bullet", "n"))

@@

The feasibility of a database of ballistic images was evaluated in a 2008 report \cite{nap:2008} by the National Research Council. The evaluation was investigating the scalability of NIBIN (National Integrated Ballistic Information Network), which uses proprietary matching algorithms provided by IBIS. The bottomline of the report was that in spite of the many technical and practical hurdles, solutions to all but one problem could be found. The remaining problem is simply that statistically the quality of the matching algorithm could not withstand a hugely increased number of records while still maintaining a reasonable workload for forensic examiners, who have to examine possible matches suggested by the system. 
The findings of the NRC report on ballistic imaging are based on two-dimensional greyscale images, which the committee argued were not reliable enough for distinguishing extremely fine marks. 
The report also found, that results from 2d images are improved upon by matches based on 3d images. This is consistent with the importance of features found here: out of the top six features in Table~\ref{tab:importance}, only the number of matches and mismatches are available for a match based on 2d features.

By suggesting an automated algorithm that first identifies lands, then identifies peaks and valleys on this land, we reduce subjectivity and with it possible sources of bias. [T]`he concept of counting striations is subjective and based on experience, but it does tend to be consistent within a single examiner' \cite{miller:1998}.
For a fair assessment of the adequacy of an algorithm we need transparency. Our matching  algorithm is open: the code is readily available in form of the R package x3rplus \cite{x3prplus}, and the code to produce this paper is available at \hh{XXX, Eric ... we need a website}. Obviously, this is only a first step, but in times of the Netflix challenge and the many Data Science challenges hosted by Kaggle, we should not let the quality of the matching algorithm be the problem that stands in the way.

@@

\paragraph{Acknowledgment} Thanks to the men and women behind the software R\cite{R}, and the authors of the R packages  knitr \cite{knitr} and ggplot2 \cite{ggplot2}.

>>>>

% Rough outline:
% \begin{enumerate}
% \item DONE Description of the problem: Standard operating practice, 2009 NAS report
% \item DONE Description of the Results
% \item DONE Walkthrough of the process
% \item \hh{XXX Alternative approaches: IBIS database and the NRC report\cite{nap:2008} against it\footnote{Fox report on the NRC report \url{http://goo.gl/XurSVl}.
% NRC report: \url{http://www.nap.edu/catalog/12162/ballistic-imaging}} }
% \end{enumerate}

Bullet matching is a process in forensic science done to determine whether two bullets were fired from the same gun barrel. This process has broad applicability in terms of the conviction of criminals in the United States criminal justice system. Ballistics identification has long been considered an accepted and reliable procedure, but in the past ten years has undergone more significant scrutiny. In 2005, in \emph{United States vs. Green}, the court ruled that the expert could not confirm that the bullet casings came from a specific weapon with certainty, but could merely describe other casings which are similar. Further court cases in the late 2000s expressed caution about the use of ballistics identification evidence~\cite{giannelli:2011}.

The new scrutiny of the procedure culminated with the 2009 National Academy of Sciences report~\cite{NAS:2009}. The report concluded that minimal research had been done exploring the reliability of these ballistic identification methods. In fact, the report says the forensic evidence ``including, for example, bite marks and firearm and toolmark identification is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline."

Rifling in the barrel creates striation marks on the bullet during the firing process (and grooves). These marks are claimed to be unique to the barrel, as described in a 1992 AFTE article~\cite{afte:1992}. ``The theory of identification as it pertains to the comparison of toolmarks enables opinions of common origin to be made when the \emph{unique surface contours} of two toolmarks are in sufficient agreement" The article goes on to state that ``Significance is determined by the comparative examination of two or more sets of surface contour patterns comprised of individual peaks, ridges and furrows." %\footnote{\url{https://www.ncjrs.gov/app/publications/Abstract.aspx?id=254151}}

@@

\section{Methodology}
Throughout this paper, we will work with images from the James Hamby Consecutively Rifled Ruger Barrel Study~\cite{hamby:2009}. Ten consecutively rifled Ruger P-85 pistol barrels were obtained from the manufacturer and fired to produce known test bullets and unknown bullets for comparison.

@@

The ``smoothing factor" described in the algorithm represents the window size to use for a rolling average. Higher values of the smoothing factor therefore lead to more smoothed results. In the groove detection portion of this algorithm, we wish to remove most of the deviation but still maintain enough signal in the groove to detect it. Empirically, a value of 35 for the smoothing factor seems to work quite well (later in the manuscript we investigate varying the smoothing factor). It is important to note that the smoothing pass is done twice. That is, the smoothed data is once again smoothed by computing a new rolling average with the same smoothing factor. This bears some similarities to the ideas of John Tukey in his book Exploratory Data Analysis, where he describes a smoothing process called ``twicing" in which a second pass is made on the residuals computed from the first pass and then added back to the result~\cite{tukey:1977}. This has the effect of introducing a little bit more variance into the smoothed data. We instead performed a second smoothing pass on the smoothed data, which has the effect of weighting observations near the center highest, while the weights linearly drop off as you reach the end of the smoothing window or smoothing factor.

@@

\section{Web Application}
We have implemented a web interface to automate many of the steps outlined in the previous section. The web interface, developed using Shiny~\cite{shiny}, allows a user to upload two x3p files representing scans of a bullet between two grooves. A 3D viewer, using Plotly~\cite{plotly}, allows the user to rotate and zoom to examine surface features of the images. A screenshot of the application is available in Figure \ref{fig:app}. The application is available at the url \url{http://erichare.shinyapps.io/x3prproto}.

@@

Figure~\ref{fig:match} gives an overview of the automated matching routine: 
We first identify a stable region for each bullet and pick the lowest crosscut level in this region, because typically, individual characteristics are best express at the lower end of the bullet. 
%\hh{(assumption here: lower crosscut levels show better expression of individual marks XXX checked XXX crosscuts-and-sd.R)}

All of the other steps are done on pairs of bullet lands:
\begin{enumerate}
\item Smooth the two crosscuts by a loess with a very small span (see Figure~\ref{fig:smooth}). 
\item Use cross-correlation to find the best alignment along the crosscuts: Shift one of the crosscuts by the lag indicated by the cross-correlation function (see Figure~\ref{fig:ccf} for the cross-correlation function and Figure~\ref{fig:crosscutX} for the resulting shift).
\item Using a rolling average, identify peaks and grooves for each of the crosscuts. We define a region around the extrema on each side as one third of the distance to the next extrema (see Figure~\ref{fig:smoothcutb}). 
\item Match grooves and peaks between crosscuts: based on the regions around the extrema as defined above, we identify joint regions between two crosscuts as those areas, in which at least two of the individual regions touch. A joint region is defined as the smallest interval that covers all of the touching regions. A joint region is called a match between the crosscuts, if all of the crosscut-specific regions are of the same type of extrema, i.e.\ either all peaks or all valleys. In Figure~\ref{fig:match} all matches are colored corresponding to their type of extrema. Non-matching regions are left grey.
\item Identify the maximal number of CMS (consecutive matching striae) between the two crosscuts by counting consecutive matching lines. 
In the example of Figure~\ref{fig:match}, the number of consecutive matching striations (CMS) is fifteen, a  high number indicative of a match between the bullets. For lead bullets, such as this, Biasotti~\cite{biasotti:1959} considered four or more consecutive lines to be sufficient evidence of a match, and which are part of current practice in assessing bullet matches ~\cite{nichols:1997, nichols:2003}.
\end{enumerate}

@@

Figure~\ref{fig:cms} shows the strong connection between the maximal number of consecutive striae and matches in the Hamby study. All 29 pairs of lands with at least sixteen CMS in common are matches. There are two things that should be noted at this point: the automated algorithm finds a relatively high number of CMS even for non-matches. On average, there are 2.2 maximal CMS between known non-matches (with a standard deviation of 1.4). Known matches share on average 8.2 maximal CMS, with a standard deviation of 5.8. Secondly, a large number of maximal CMS by itself is not indicative of a match, as was previously pointed out by Miller~\cite{miller:1998}. Figure~\ref{fig:mismatch} shows a known mismatch, between two lands that share fifteen consecutively matched striae. The number of peaks and valleys, their heights and depths as well as the overall pattern are in relative good agreement. \hh{XXX something re-assuring that visually we can tell them apart? I don't know - this could just as well be a case where the crosscuts are very different. }
%
\begin{figure}[hbtp]
\begin{subfigure}[t]{\linewidth}
\caption{Distribution of maximal CMS.}
<<cms-bars, echo=FALSE, fig.width=7, fig.height=3.5, out.width='\\linewidth'>>=
bstats <- read.csv("data-35-25/bullet-stats.csv")
ggplot(data=bstats) + 
  geom_bar(aes(x=factor(cms))) + theme_bw() +
  theme(legend.position="bottom") + 
  xlab("maximum CMS")
@
\end{subfigure}
\begin{subfigure}[t]{\linewidth}
\caption{All land-to-land comparisons a maximum number of CMS of sixteen or more are matches.}
<<cms-spines, echo=FALSE,  fig.width=7, fig.height=3.5, out.width='\\linewidth'>>=
ggplot(data=bstats) + 
  geom_bar(aes(x=factor(cms), fill=match), position="fill") +
  theme(legend.position="bottom") + 
  scale_fill_brewer(palette="Paired") +
  xlab("maximum CMS")
@
\end{subfigure}
\caption{\label{fig:cms}Overview of the maximal number of consecutive maximal striae compared to matches.}
\end{figure}

@@

Using recursive partitioning, we fit a decision tree~\cite{breiman:1984, rpart, rpart.plot} to predict matches between lands based on features derived from the image files. The resulting tree is shown in Figure~\ref{fig:tree}. A total of 123 lands is being matched correctly. Interestingly, the number of consecutive matching striae only features as the last step in this evaluation. At this point in the tree, the first false positive matches are introduced into the results: out of the ten land-to-land comparisons three are mis-matched.
Instead of CMS, cross-correlation (ccf) between the crosscuts is very important in the matching process  by the decision tree. Aside from  cross correlation, the number of matches (num.matches) between crosscuts and the distance between crosscuts (distr.dist) is involved in the decision. 
Within matches and non-matches, the values of CMS and cross-correlation seem to be almost independent (see Figure~\ref{fig:ccfs-match}), but both are highly predictive in distinguishing matches from non-matches. Out of the two, cross-correlation has higher  predictive power. This  does not  contradict earlier findings emphasizing the value of CMS on visual assessments of bullet matches: in those papers, assessments were based on purely visual inspection of either actual bullets or 2d microscopic images of bullets.
Neither one of these methods allows for an assessment of cross-correlations. This is one of the benefits of switching to a digitalized version of the images that preserves the 3d surface structure.

@@

Another benefit is that we can not only apply a single decision tree, but several hundred of them to combine in a random forest~\cite{breiman:2001, randomForest}. In a random forest multiple trees are fitted. For each of these trees, only two thirds of the observations are used for fitting, while predictions for the remaining third  are used to evaluate the tree's predictive power and accuracy, or its reverse, the error rate. Because errors are determined from the one third of held-back observations, this error rate is called the out-of bag (OOB) error. 
Figure~\ref{fig:oob} shows the cumulative out-of-bag error (OOB) rate for 300 trees. 
%
\begin{figure}[hbtp]
<<oob, echo=FALSE, fig.width=7, fig.height=3, out.width='\\linewidth'>>=
qplot(id, OOB, geom="line", data=errors) + theme_bw() + ylim(c(0,NA)) + xlab("Number of trees") + ylab("Out of Bag Error (OOB)")
@
\caption{\label{fig:oob}Cumulative out-of-bag error rate of a random forest fit to predict land-to-land matches from image features.}
\end{figure}
%
After about 25 trees, the error rate of land-to-land comparisons stabilizes at 0.0056. This is a weighted average between false positives of 0.00028 and false negatives of 0.32. Note that these error rates are based on land-to-land comparisons and will be much lower for bullet-to-bullet matches. In the case of the Hamby study, the error rate is zero, if we require for a bullet match that at least two of a bullet's lands are matched (see Figure~\ref{fig:treeresult}). 
\begin{figure}[hbtp]
<<overall-tree, echo=FALSE, fig.width=7, fig.height=4, out.width='\\linewidth'>>=
CCFs$bullet <- gsub("-[0-9]$", "", CCFs$b2)
bullets <- CCFs %>% group_by(bullet) %>% summarize(
  n = n(),
  pred = sum(pred > 0.5),
  forest = sum(forest > 0.5)
)
library(reshape2)
bm <- melt(data=bullets, id.var=c("bullet", "n"))

@@

The feasibility of a database of ballistic images was evaluated in a 2008 report~\cite{nap:2008} by the National Research Council. The evaluation was investigating the scalability of NIBIN (National Integrated Ballistic Information Network), which uses proprietary matching algorithms provided by IBIS. The bottomline of the report was that in spite of the many technical and practical hurdles, solutions to all but one problem could be found. The remaining problem is simply that statistically the quality of the matching algorithm could not withstand a hugely increased number of records while still maintaining a reasonable workload for forensic examiners, who have to examine possible matches suggested by the system. 
The findings of the NRC report on ballistic imaging are based on two-dimensional greyscale images, which the committee argued were not reliable enough for distinguishing extremely fine marks. 
The report also found, that results from 2d images are improved upon by matches based on 3d images. This is consistent with the importance of features found here: out of the top six features in Table~\ref{tab:importance}, only the number of matches and mismatches are available for a match based on 2d features.

By suggesting an automated algorithm that first identifies lands, then identifies peaks and valleys on this land, we reduce subjectivity and with it possible sources of bias. [T]`he concept of counting striations is subjective and based on experience, but it does tend to be consistent within a single examiner'~\cite{miller:1998}.
For a fair assessment of the adequacy of an algorithm we need transparency. Our matching  algorithm is open: the code is readily available in form of the R package x3rplus~\cite{x3prplus}, and the code to produce this paper is available at \hh{XXX, Eric ... we need a website}. Obviously, this is only a first step, but in times of the Netflix challenge and the many Data Science challenges hosted by Kaggle, we should not let the quality of the matching algorithm be the problem that stands in the way.

@@

\paragraph{Acknowledgment} Thanks to the men and women behind the software R~\cite{R}, and the authors of the R packages  knitr~\cite{knitr} and ggplot2~\cite{ggplot2}.
